%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{portrait}
\name{\Huge Rareș}{\Huge\ Anghel-Stan}
\position{Mathematician/Software Developer}
\address{Laan van avant garde, Rotterdam}
\mobile{(+40) 769 159 135}
\email{rares1928.de@gmail.com}
\homepage{www.rares-stan.ro}
%\github{rares1928}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}



%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {ACT}
  {Amsterdam, Netherlands}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Quantitative Risk Analyst}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,\\ Rareș Anghel-Stan}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}
  {}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
In my previous role as a Software Developer at Diomedes-technologies, a high-frequency trading firm, I improved my skills in scientific programming and data analysis. I successfully parsed and analysed large datasets using Python and SQL, developed statistical models to derive key metrics, and implemented automated processes to enhance data quality and efficiency. 

Prior to that, I learned how to code by developing a website for medical school graduates in Romania to help them prepare for their final exams. I built the front-end using JavaScript and React (Material-UI) and developed the back-end with Azure Functions (C\#) and SQL. Additionally, I integrated Stripe to handle the payment system. The front-end code can be found at: \url{https://github.com/rares1928/rezigo_v2}.

My academic background includes a Ph.D. in Mathematics from the Mathematics Institute of the Romanian Academy, where I specialised in spectral and algebraic methods in the study of differential manifolds. I also attended several machine learning seminars where I understood the density of functions created by neural networks (with architectures that can have either only one hidden layer or multiple hidden layers) in the set of continuous functions.


\lettersection{Why ACT?}
I am writing to express my interest in the Quantitative Risk Analyst position in Amsterdam. My motivation comes from my willingness to solve real-world problems as well as my desire to constantly improve. With my background in mathematics and experience in software development, I am excited about the opportunity to work as an analyst for ACT. I would love to put my problem-solving skills to the test by tackling challenges that arise in generating high quality predictive signals, as well as implementing these ideas. I also value collaboration and have experience working closely with various stakeholders to ensure the successful execution of projects

\lettersection{Why Me?}
My research experience has equipped me with strong analytical and problem-solving skills, while my previous role as a Software Developer provided hands-on experience in implementing my ideas and solutions. I am proficient in reading, understanding, and adapting ideas from the latest research papers. In a field that evolves as rapidly as software development, the ability to grasp and adapt to new breakthroughs is imperative. I have experience optimizing algorithms and building predictive models, which I am eager to apply in risk prediction and developing strategies to mitigate financial risks at ACT. Additionally, my curiosity and passion for data analysis, combined with a fast-learning mindset, make me eager to tackle complex challenges in a high-performance environment. I am confident that my blend of technical expertise, research experience, and passion for data analysis will allow me to contribute meaningfully to ACT's success, and I am eager to bring my skills to your dynamic team.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
